---
title: DANL Project
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Alex Ventresca
  - Ann Brennan
  - Drew Cox

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About this project :clap:

This project will address the various financial actions taken by various parties to address climate change. 

# Variable Description

Party: a party (country) that provides a funding contribution to recipient country/region for their cliamte change project.

Recipient country/region: Recipient country or region

Project/programme/activity: Details in the climate change project

Type of support:adaptation if the climate change project is related to adaptation project. mitigation if the climate change project is related to mitigation project.

Year: Year that funding contribution is committed or provided.

Contribution: An amount of funding contribution for the climate change project (in USD).

Status: committed if a party commits to providing the funding contribution for the climate change project, but the funding contribution is NOT actually provided.
provided if the funding contribution was provided for the climate change project.

Energy: TRUE if the project is energy-related; FALSE otherwise.

# Data

The data.frame 'climate_finance' contains data regarding the statuses of parties and their funding contributions for addressing climate change, adapted from the United Nations Climate Finance page (https://unfccc.int/topics/introduction-to-climate-finance).

 :oncoming_automobile:


## Summary Statistics

```{r}
path <- 'https://bcdanl.github.io/data/climate_finance_energy.csv'
climate_finance <- read_csv(path)

#| results: asis
#| echo: false
rmarkdown::paged_table(climate_finance) 
```


```{r}
skim(climate_finance) %>% 
  select(-n_missing)
```


## Summary of Contribution for Adaptation Projects
8 countries have provided positive financial contributions to other countries / regions for their adaptation projects for every year between 2011 and 2018. :blue_car: :truck: :minibus:.


```{r}
Q1a <- climate_finance %>% 
  filter(Status == "provided",                       
         `Type of support` == "adaptation") %>%      
  group_by(Party, Year) %>%                          
  summarise(Contribution = sum(Contribution, na.rm = T)) %>%  
  filter(Contribution > 0) %>%                       
  group_by(Party) %>%                                
  count() %>%                                        
  filter(n == 2018 - 2011 + 1)  %>%                  
  select(Party) %>% 
  distinct()     
```

## Yearly Contribution varying by Energy and Status
For both sectors (energy and non-energy), the amount of the committed funding has been increasing yearly, while the amount of provided funding has stayed relatively constant. Energy related projects usually require a much greater upfront cost than non-energy related projects, hence why there is a gap for the provided amounts. 


```{r}
climate_finance %>% 
  group_by(Energy, Status, Year) %>% 
  summarise(funding_tot = sum(Contribution, na.rm = T)) %>% 
  ggplot(aes(x = Year, y = funding_tot)) +
  geom_line(aes(color = Status)) +
  geom_point() +
  facet_wrap(Energy ~.) +
  scale_y_comma()
```


## Distribution of ratio between adaptation and mitigation contributions


```{r}
Q1c <- climate_finance %>% 
  group_by(Party, Year, Status, `Type of support`) %>% 
  summarise(Contribution = sum(Contribution, na.rm = T)) %>% 
  filter(Contribution != 0) %>% 
  group_by(Party, Year, Status) %>% 
  mutate(lag_Contribution = lag(Contribution), 
         am_ratio = lag_Contribution / Contribution ) %>% 
  filter(!is.na(am_ratio)) %>% 
  rename(mitigation = Contribution, 
         adaptation = lag_Contribution) %>% 
  select(-`Type of support`)  

Q1c <- climate_finance %>% 
  group_by(Party, Year, Status) %>%  
  summarise(adaptation = sum(Contribution[`Type of support` == 'adaptation'], na.rm = T), 
            mitigation = sum(Contribution[`Type of support` == 'mitigation'], na.rm = T)
            ) %>% 
  filter(adaptation != 0, mitigation != 0) %>% 
  mutate(am_ratio = adaptation / mitigation ) 

ggplot(Q1c, aes(x = log(am_ratio))) +
  geom_histogram(bins = 75) +
  geom_vline(xintercept = 0, color = 'red', lty = 2)
```


## Contribution varying by Type of Support and Status
For the amount of countries that have committed to support climate funding, meaning they have pledged to pay but have not actually provided any funding, the count is similar for adaptation versus mitigation projects. For countries that have actually provided contribution funds, the count is much higher for adaptation projects compared to mitigation projects. 


```{r}
ggplot(climate_finance,
       aes(color = `Type of support`, x = log(Contribution))) +
  geom_freqpoly() +
  facet_wrap(.~ Status)
```

# Summary

There is not one set path or action to take to solve the climate change crisis, as demonstrated by the various amounts and types of funding actions. Climate finance is a complicated subject, but to solve the problem, more action (such as actually providing funds instead of just committing to it) is needed by all parties. 